Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-07-31 Documents/Paper/ms.tex
Equation for galaxy

In this section we apply
the DNS approach to a toy version of the problem of detecting and quantifying
extended objects such as galaxies in a noisy image.

We model each galaxy as a mixture of two concentric elliptical galaxies, with
the following eight parameters. Firstly, two
parameters $x_c$ and $y_c$ describe the central position of the galaxy within
the image. The flux $f$ describes the total integral of the galaxy's
intensity profile. The axis ratio $q$ describes the ellipticity of the galaxy
and $\theta$ its orientation angle with respect to horizontal. Finally
we include a ``radius ratio'' $u$ describing the ratio of the radius of the
smaller gaussian with respect to that of the bigger gaussian, and a parameter
$v$ describing the fraction of the total flux in the outer gaussian
(therefore the fraction of the light in the smaller gaussian is $1-v$).

>>>>

In this section we apply
the DNS approach to a toy version of the problem of detecting and quantifying
extended objects such as galaxies in a noisy image.
We model each galaxy as a mixture of two concentric elliptical components, with
the following eight parameters. Firstly, two
parameters $x_c$ and $y_c$ describe the central position of the galaxy within
the image. The flux $f$ describes the total integral of the galaxy's
intensity profile. The axis ratio $q$ describes the ellipticity of the galaxy
and $\theta$ its orientation angle with respect to horizontal. The radius of the
bigger gaussian is a parameter $a$.
Finally
we include a ``radius ratio'' $u$ describing the ratio of the radius of the
smaller gaussian with respect to that of the bigger gaussian, and a parameter
$v$ describing the fraction of the total flux in the smaller gaussian
(therefore the fraction of the light in the bigger gaussian is $1-v$).
In a coordinate system aligned with the major axis of the ellipse, the
surface brightness profile of a ``galaxy'' is given by
\begin{eqnarray}
\rho(x, y) &=&
\frac{f(1-v)}{2\pi a^2}\exp\left[-\frac{1}{2a^2}\left(qx^2 + y^2/q\right)\right]
+\frac{fv}{2\pi (ua)^2}\exp\left[-\frac{1}{2(ua)^2}\left(qx^2 + y^2/q\right)\right]
\end{eqnarray}
